Distributed Algorithms for Sparse Matrix-Vector Multiplication

### 2015-04-27 presentation.Rmd
Small changes to pres
Just some tweaks to the slides

## Outline
- Statistics Background
- Load Balanced Sparse Matrix-Multiplication
- Architecture-aware Technique
- Scalable Parallel Matrix Multiplication

@@

@@

## Highly Skewed Data
In a matrix that is both highly skewed and highly sparse, splitting rows that have a significantly larger number of non-zero elements is necessary. This incurs a slight overhead and hence is only recommended for more extreme cases.

@@

@@

>>>>

## Outline
- SpMV Overview
- Statistics Background
- Load Balanced Sparse Matrix-Multiplication
- Architecture-aware Technique
- Scalable Parallel Matrix Multiplication

## SpMV Overview
Typically, Matrices are stored with **two-dimensional arrays**.

But, for matrices that are **sparse** (contain a lot of zeroes), this is not ideal:
- Waste of memory
- Waste of computation time - Lots of multiplications and additions of zero

## SpMV Methods
Matrix/vector multiplication is a highly parallelizable task, but if we naively distribute these computations out to processors, we compound the issues of sparsity - Very uneven workload!

@@

Further, we often have a design matrix that is held constant ($X$) across several iterations of the experiment, but a response vector $y$ that may change frequently as new sets of data are collected and analyzed.

@@

## Highly Skewed Data
- In a matrix that is both highly skewed and highly sparse, splitting rows that have a significantly larger number of non-zero elements is necessary.

- This incurs a slight overhead and hence is only recommended for more extreme cases.

@@

## Conclusion
One of the first distributed advances of this problem - Successful, widely used, but perhaps less relevant than now due to GPU-level improvements.

@@

## Conclusion
- Incremental speedup
-
